Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-15 acks.tex
added ack for Mozilla gift

The authors would like to thank the anonymous referees at POPL and TFP 2016  for useful feedback on earlier drafts of this paper; Ed Morehouse and Carlo Angiuli for counsel on mechanization and Barendrecht's
Convention; Vincent Zeng for \textit{pro bono} artistic services; and YoungSeok Yoon for reanalyzing the data from \cite{6883030}. 
%This is Danny Dig's COPE grant. He asked me to add the grant.
This work was partially funded through the NSF grant \#CCF-1439957; by AFRL and DARPA under agreement \#FA8750-16-2-0042; and by NSA lablet contract \#H98230-14-C-0140. The views and conclusions contained herein are those of the authors and should not be interpreted as necessarily representing the official policies or endorsements, either expressed or implied, of the NSF, AFRL, DARPA, the NSA or the U.S. Government.

>>>>

The authors would like to thank the anonymous referees at POPL and TFP 2016  for useful feedback on earlier drafts of this paper; Ed Morehouse and Carlo Angiuli for counsel on mechanization and Barendrecht's
Convention; Vincent Zeng for \textit{pro bono} artistic services; and YoungSeok Yoon for reanalyzing the data from \cite{6883030}.
%This is Danny Dig's COPE grant. He asked me to add the grant.
This work was partially funded through a gift from Mozilla; the NSF grant \#CCF-1553741 and 1439957; by AFRL and DARPA under agreement \#FA8750-16-2-0042; and by NSA lablet contract \#H98230-14-C-0140. The views and conclusions contained herein are those of the authors and should not be interpreted as necessarily representing the official policies or endorsements, either expressed or implied, of Mozilla, the NSF, AFRL, DARPA, the NSA or the U.S. Government.

### 2016-11-15 agda.tex

In order to
formally establish that our design meets our stated objectives, we have
mechanized the semantics and metatheory of Hazelnut as described above (and more concisely in the appendix) using the Agda proof
assistant \cite{norell:thesis} (also see the Agda Wiki, hosted
at \url{http://wiki.portal.chalmers.se/agda/}.) This development is available in the supplemental material. The mechanization also includes the  extension to the
language described in Sec. \ref{sec:extending}.

>>>>

In order to
formally establish that our design meets our stated objectives, we have
mechanized the semantics and metatheory of Hazelnut as described above using the Agda proof
assistant \cite{norell:thesis} (also see the Agda Wiki, hosted
at \url{http://wiki.portal.chalmers.se/agda/}.) This development is available in the supplemental material. The mechanization also includes the  extension to Hazelnut described in Sec. \ref{sec:extending}.
